Template for PRL/PRD Papers

### 2019-10-09 DNP_Meetings/abstract/abstract.tex
updated DNP

\small
for the Hall C Collaboration

@@

\noindent Preliminary D(e,e'p)n electro-disintegration cross sections at $Q^{2} = 4.25$ GeV$^{2}$ with recoil
momenta up to 900 MeV/c will be presented. The experiment ran for a total of 6 days of beam time in April 2018
at Jefferson Lab in Hall C and it seeks to study the short range structure of the deuteron by probing its high
momentum components beyond 500 MeV/c, where currently no data exists. The experiment was part of a group of Hall C
experiemnts that commissioned the new Hall C Super High Momentum Spectrometer (SHMS). At the selected kinematics,
Meson Exchange Currents (MEC) and Isobar Configurations (IC) are suppressed. Final State Interactions (FSI) have also
been suppressed by choosing a kinematic region where the neutron recoil angle is between 35 and 45 degrees with respect
to the momentum transfer. This suppression was seen in a previous D(e,e'p)n experiment (Boeglin et al. Phys Rev Lett. 2011)
and is also predicted in modern theoretical calculations (W. Boeglin \& M. Sargsian Int.J.Mod.Phys. 2015). In this region,
the Plane Wave Impulse Approximation (PWIA) dominates and comparisions between measured and predicted cross sections are
sensitive to the deuteron momentum distributions. Comparisons between data and different calculations with different NN
potentials will be shown.

>>>>

\small
Spokespeople: Drs. Werner U. Boeglin and Mark K. Jones

@@

\noindent Preliminary D(e,e'p)n electro-disintegration cross sections at $Q^{2} = 4.25$ GeV$^{2}$ with recoil momenta up to 900 MeV/c will be
presented. The experiment ran for a total of 6 days of beam time in April 2018 at Jefferson Lab in Hall C
and it seeks to study the short range structure of the deuteron by probing its high momentum tails
beyond 500 MeV/c, where currently no data exists. The experiment was part of a group of Hall C experiemnts that commissioned the
the new Hall C Super High Momentum Spectrometer (SHMS). At these kinematics, Meson Exchange Currents (MEC) and Isobar Configurations (IC)
are suppressed. Final State Interactions (FSI), however, can be important. From theoretical calculations by M. Sargsian in
"Modern Studies of the Deuteron: from the Lab Frame to the Light Front" (Boeglin, W.U. and Sargsian, M.M. Int.J.Mod.Phys. 2015),
FSI can be suppressed by choosing a kinematic region where the neutron recoil angle is between 35 and 45 degrees. This suppression
was seen in a previous D(e,e'p)n experiment that went to recoil momentum of 500 MeV/c. See for example, "Probing the High Momentum Component
of the Deuteron at High Q2" (Boeglin, W.U. et al. Phys Rev Lett. 2011). In this region, the Plane Wave Impulse Approximation (PWIA) is valid
and comparisions between measured and predicted cross sections have a sensitivity to the different NN potentials. Comparisons between the data
and different theory calculations with different NN potentials will be shown.

### 2019-10-09 MY_PUBLICATIONS/latex_templates/prl.tex
updated DNP

%% ****** Start of file template.aps ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.0 of REVTeX, August 2001
%%
%%
%%   Copyright (c) 2001 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math

% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

To cite bibliography entries, use the \verb+\cite{#1}+ command. Most
journal styles will display the corresponding number(s) in square
brackets: \cite{d0det}. To avoid the square brackets, use
\verb+\onlinecite{#1}+: Refs.~\onlinecite{d0det} and
\onlinecite{geant,pythia}. REV\TeX\ ``collapses'' lists of
consecutive reference numbers where possible. We now cite everyone
together \cite{geant, pythia, cteq}, and once again
(Refs.~\onlinecite{geant, pythia, cteq}). Note that the references
were also sorted into the correct numerical order as well.

@@

\begin{thebibliography}{99}

  \bibitem{d0det}
    Standard D\O\ detector reference:  \\
V.M.~Abazov {\sl et al.} (D0 Collaboration),
Nucl. Instrum. Methods Phys. Res. A {\bf 565}, 463  (2006).

  \bibitem{d0lumi}
    ** New ** D\O\ luminosity reference: \\
T.~Andeen {\sl et al.}, FERMILAB-TM-2365 (2007).

  \bibitem{pdg}
   Particle Data Group reference: \\
   W.-M.~Yao {\sl et al.}, Journal of Physics G {\bf 33}, 1 (2006).

  \bibitem{geant}
    {\sc Geant} reference: \\
    R. Brun and F. Carminati, CERN Program Library Long Writeup W5013, 1993 (unpublished).

  \bibitem{pythia}
    {\sc Pythia} reference: \\
    T. Sj\"{o}strand {\sl et al.}, Comput. Phys. Commun. {\bf 135}, 238 (2001).

  \bibitem{cteq}
    {\sc Cteq6} reference: \\
    J. Pumplin {\sl et al.}, JHEP {\bf 0207} 012 (2002) and
    D. Stump {\sl et al.}, JHEP {\bf 0310} 046 (2003).

  \bibitem{cls}
    LEP CL$_S$ reference: \\
    T. Junk, Nucl. Instrum. Methods A {\bf 434}, 435 (1999).

  \bibitem{d0limit}
   D\O\ Bayesian reference: \\
   I. Bertram {\sl et al.}, FERMILAB-TM-2104 (2000).

  \bibitem{d0jets}
  D\O\ cone-jet reference: \\
G.C.~Blazey {\it et al.}, in
{\sl Proceedings of the Workshop: QCD and Weak Boson
Physics in Run II,} edited by U.~Baur, R.K.~Ellis, and
D. Zeppenfeld, Fermilab-Pub-00/297 (2000).

\end{thebibliography}

>>>>

%% ****** Start of file template.aps ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.0 of REVTeX, August 2001
%%
%%
%%   Copyright (c) 2001 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4-1}  % for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}  % for double-spaced preprint
\usepackage{graphicx}  % needed for figures
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!80!black},
    urlcolor={blue!80!black}
}
% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

To cite bibliography entries, use the \verb+\cite{#1}+ command. Most
journal styles will display the corresponding number(s) in square
brackets: \cite{d0det}. To avoid the square brackets, use
\verb+\onlinecite{#1}+: Refs.~\onlinecite{d0det} and
\onlinecite{geant,pythia}. REV\TeX\ ``collapses'' lists of
consecutive reference numbers where possible. We now cite everyone
together \cite{geant, pythia, cteq}, and once again
(Refs.~\onlinecite{geant, pythia, cteq}). Note that the references
were also sorted into the correct numerical order as well.
\cite{einstein}

@@

\bibliography{prl}
